Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-09 paper.tex
Import.

on the trained object.

@@

As an example, let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as:
% XXX: Gael: I think that we should break the following lines in 2: the
% 'return self' hidden in the call to fit can be confusing to the casual
% reader
\begin{verbatim}
clf = LogisticRegression(penalty="l1")
clf.fit(X_train, y_train)
\end{verbatim}
In this snippet, a \texttt{LogisticRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{l1}, hence
enabling $\ell_1$
regularization, and using default values for all other hyper-parameters. Upon
\texttt{fit}, the model is then learned from the training arrays \texttt{X\_train} and
\texttt{y\_train}. Also, since all estimators share the same interface, using a
different learning algorithm is as simple as replacing the constructor. For
example, to build a Random Forest on the same training data, one would simply
have to replace \texttt{LogisticRegression(penalty="l1")} in the snippet above by
\texttt{RandomForestClassifier()}.

>>>>

@@

As an example, let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as:
% XXX: Gael: I think that we should break the following lines in 2: the
% 'return self' hidden in the call to fit can be confusing to the casual
% reader
\begin{verbatim}
from sklearn.linear_model import LogisticRegression
clf = LogisticRegression(penalty="l1")
clf.fit(X_train, y_train)
\end{verbatim}
In this snippet, a \texttt{LogisticRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{"l1"}, hence enabling
$\ell_1$ regularization. Other hyper-parameters (such as \texttt{C}, which
defines the strength of the regularization) are not explicitly defined and are
thus set to the default values. Upon calling \texttt{fit}, the model is then
learned from the training arrays \texttt{X\_train} and \texttt{y\_train}. Since
all estimators share the same interface, using a different learning algorithm is
as simple as replacing the constructor. For example, to build a Random Forest on
the same training data, one would simply have to replace
\texttt{LogisticRegression(penalty="l1")} in the snippet above by \\
\texttt{RandomForestClassifier()}.
